\chapter{Project Proposal \\
\small{\textit{-- Nataly Jimenez, Nicole Valdiviezo, Lakshya Vegiraju}}
\index{Project Proposal} 
\index{Chapter!Project Proposal}
\label{Chapter::Project Proposal}}

\section*{Project Title}
HTML Drawings Dance to Music

\section*{Project Description}
The goal of this project is to create a dynamic web-based application that combines audio and visual elements using vanilla JavaScript and the HTML5 Canvas element. The application will allow shapes and colors to move and transform in response to music, ultimately producing beautiful audio visualizations.  

A sample task includes building an interactive music visualizer that reacts in real time to user-selected audio files. The project will start from the basics of drawing shapes on a canvas and gradually progress to more advanced features such as frequency analysis, animation techniques, and synchronization with audio events.  

The project will also explore integrating DevSecOps tools to manage the lifecycle, ensuring secure, maintainable, and automated development practices.  

\subsection*{Potential DevSecOps Tools}
\begin{itemize}
    \item \textbf{Source Control:} GitHub for version control and collaborative development.
    \item \textbf{Testing:} Jest (JavaScript testing framework) to validate audio analysis and canvas rendering functions.
    \item \textbf{Deployment:} GitHub Pages or AWS Amplify for hosting the web application.
    \item \textbf{Databases:} (Optional) Firebase or AWS DynamoDB for saving user preferences, visualizer settings, or playlists.
    \item \textbf{CI/CD Pipelines:} GitHub Actions for automated builds, testing, and deployments.
    \item \textbf{Monitoring:} AWS CloudWatch or open-source tools like Grafana/Prometheus for operational monitoring.
    \item \textbf{Security:} Dependabot (via GitHub) for vulnerability scanning, ESLint for secure code checks.
\end{itemize}

\section*{Expectations / Rubric}
The project will be evaluated based on the following criteria:

\begin{enumerate}
    \item \textbf{Selected Tool(s) or Environment} 
    \item \textbf{Building a Sample Working Application (40 pts)}  
    Development of an HTML5 Canvas audio visualizer application.
    
    \item \textbf{Using Specific Tools (DevOps tools) (20 pts)}  
    Integration of version control (GitHub), testing (Jest), deployment (AWS Amplify vs GitHub Pages), and monitoring tools. A comparison will be made between two hosting solutions.
    
    \item \textbf{Environment to Build the Project (20 pts)}  
    Hosting on AWS Amplify and GitHub Pages, with automated pipelines (GitHub Actions).
    
    \item \textbf{Operational Dashboard (20 pts)}  
    A monitoring dashboard (Grafana or CloudWatch) to reflect performance and operational aspects of the web app.
    
    \item \textbf{SWOT Chart (20 pts)}  
    A customized SWOT analysis for each major tool (e.g., GitHub Pages vs AWS Amplify).
    
    \item \textbf{Propose Something Unique}  
    Demonstrating real-time visualization of custom audio input (user-uploaded MP3 or live microphone input) for creative coding projects.
\end{enumerate}
